Personality and political beliefs across the lifespan

### 2019-12-11 scripts/manuscript.Rmd
Discussion

>>>>

Consistent with prior research on personality and political beliefs,  participants in this study  that were higher in economic conservatism produced significantly lower scores on openness to experience. This relationship has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience [@carney2008secret; @ekehammar2004matters].

However, inconsistent with prior research and our hypotheses, the negative relationship between social conservatism and openness to experience scores, along with the positive relationships between conscientiousness and both social and economic conservatism were not significant. With this subject so heavily studied, the lack of significant results indicates that a replication of the study that includes a power analysis and possibly, an increase in sample size may give us a clearer understanding of the strength and significance of these relationships.

Additional exploratory analysis revealed a significant positive relationship between emotional stability and social conservatism, as well as a positive relationship between agreeableness and social conservatism. Prior research indicates that emotional stability is not a significant predictor of  conservatism, and agreeableness is usually negatively correlated with conservatism [@sibley2012personality]. The departure of these results from previous findings may indicate that there is an increase in positive personality traits associated with conservatism, but the controlling, firm, inhibited characteristics heavily associated with conservatism are not compatible with the change in direction between agreeableness and conservatism.

While the results of this study did not support all of our hypotheses on personality traits and conservatism, the limitations of the study surrounding the self-reporting methods along with the potential low power of the study may help explain the departure of our results from previous findings. Future research on this subject would be more informed through the use of  experimental methods and observations of participants to determine behavior that reveals personality traits and level of social and economic conservatism. Increasing understanding of the relationship between personality traits and left-right differences could help implement actions that would help diffuse the increasing political polarization currently taking place in the United States.

### 2019-12-11 scripts/manuscript.tex
Discussion

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Personality and political beliefs across the lifespan},
            pdfauthor={Sarah Dimakis, Meghan Siritzky, \& Jamie Yellowtail},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{PERSONALITY AND POLITICAL BELIEFS}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Oregon}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{
Here is where we will write our abstract.

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
\begin{tabular}{lllll}
\toprule
Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
\midrule
Intercept & 25.82 & $[0.07$, $51.58]$ & 1.98 & .049\\
Openness to experiences & -3.73 & $[-7.50$, $0.04]$ & -1.96 & .052\\
Conscientiousness & 0.07 & $[-3.98$, $4.11]$ & 0.03 & .974\\
Extraversion & 1.56 & $[-1.42$, $4.55]$ & 1.04 & .302\\
Agreeableness & 3.93 & $[0.69$, $7.17]$ & 2.40 & .018\\
Emotional stability & 4.30 & $[0.70$, $7.91]$ & 2.37 & .020\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Residual standard error: 25.13 on 125 degrees of freedom.
Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
\begin{tabular}{lllll}
\toprule
Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
\midrule
Intercept & 56.54 & $[34.71$, $78.37]$ & 5.13 & < .001\\
Openness to experiences & -3.79 & $[-6.98$, $-0.59]$ & -2.35 & .021\\
Conscientiousness & 1.78 & $[-1.65$, $5.20]$ & 1.03 & .307\\
Extraversion & 0.61 & $[-1.92$, $3.14]$ & 0.48 & .632\\
Agreeableness & -1.13 & $[-3.88$, $1.61]$ & -0.82 & .415\\
Emotional stability & 2.34 & $[-0.71$, $5.39]$ & 1.52 & .131\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Residual standard error: 21.3 on 125 degrees of freedom. Multiple R-squared: 0.081, Adjusted R-squared: 0.044. F(5, 125): 2.207, p-value: 0.058.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.

@@

To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits. We found that together the personality traits explain about 13.5\% of the variance in social conservatism scores, \emph{F}(5, 125) = 5.05, \emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table 3). We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) = 2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30, \emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure. Additionally, openness to experiences margionally predicted social conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.

@@

@@

\begin{verbatim}
## Warning in readLines(file): incomplete final line found on 'r-
## references.bib'
\end{verbatim}

@@

@@

@@

@@

@@

@@

@@

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Personality and political beliefs across the lifespan},
            pdfauthor={Sarah Dimakis, Meghan Siritzky, \& Jamie Yellowtail},
            pdfkeywords={keywords: personality, openness to experiences, conscientiousness, extraversion, agreeableness, emotional stability, conservatism, social conservatism, economic conservatism},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{PERSONALITY AND POLITICAL BELIEFS}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Oregon}
\keywords{keywords: personality, openness to experiences, conscientiousness, extraversion, agreeableness, emotional stability, conservatism, social conservatism, economic conservatism\newline\indent Word count: 208}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{
Since the development of the Five Factor Model as a framework for measuring and classifying personality, psychology research has been interested in using this framework to examine the relationship between personality and cognitions, mindsets, and behaviors. Prior research has attempted to predict political beliefs and affiliations from personality traits, finding that the personality trait of openness to experience is positively correlated with liberalness, while the trait of conscientiousness is positively correlated with conservativeness. The current study attempts to replicate these findings in a U.S. Amazon Mechanical Turk population using the Ten Item Personality Inventory to measure the Big Five personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) and a 12-item Social and Economic Conservatism Scale to measure the social and economic dimensions of conservatism. Consistent with past research, the current study found that openness to experience was a significant negative predictor of both economic and social conservatism. Contrary to past findings, however, we found that agreeableness and emotional stability were both significant positive predictors of social conservatism, and conscientiousness was not a significant predictor of either social or economic conservatism. Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits, but they were strongly positively correlated with each other.

@@

The Five Factor Model is a widely used framework for measuring and classifying personality into five dimensions (Goldberg, 1992; John \& Srivastava, 1999; McCrae et al., 1999). Those who score high in \emph{openness to experiences} tend to describe themselves as curious, deep thinkers compared to those who score low in openness to experience, who describe themselves as traditional and conventional. Those who score high in \emph{conscientiousness} are generally reliable and hardworking, while those who score low in conscientiousness tend to be disorganized and impulsive. Those high in \emph{extraversion} are talkative and energetic, while those high in introversion are reserved and quiet. Those who score high in \emph{agreeableness} describe themselves as kind and trusting, while those who score low in agreeableness say they are quarrelsome and critical. And lastly, those who are high in \emph{emotional stability} are calm individuals who handle stress well, while those high in neuroticism tend to be anxious individuals who are easily upset.

Given that these personality traits have been found to predict a multitude of cognitions and behaviors, from well-being to cognitive abilities (Barlett \& Anderson, 2012; Curtis, Windsor, \& Soubelet, 2015; Hayes \& Joseph, 2003), previous studies have looked at whether personality can predict political beliefs and affiliation (Hirsh, DeYoung, Xu, \& Peterson, 2010; Jost, West, \& Gosling, 2009). The most robust findings are that openness to experience is positively correlated with liberalness (Carney, Jost, Gosling, \& Potter, 2008; Ekehammar, Akrami, Gylje, \& Zakrisson, 2004), while conscientiousness is positively correlated with conservativeness (Barbaranelli, Caprara, Vecchione, \& Fraley, 2007; Stenner, 2005).

This project uses data from a larger study that measured political beliefs and the big five personality traits. Consistent with prior research, we hypothesize that we will find a positive relation between conscientiousness and conservatism and a negative relation between openness to experience and conservatism. We will first make exploratory tables and plots that explore the relation between all big five personality traits and social and economic conservatism, and then we will run two linear models with traits as predictors and types of conservatism as outcome variables.

\hypertarget{method}{%
\section{Method}\label{method}}

@@

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.

@@

To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits. We found that together the personality traits explain about 13.5\% of the variance in social conservatism scores, \emph{F}(5, 125) = 5.05, \emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table 3). We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) = 2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30, \emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure. Additionally, openness to experiences marginally predicted social conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.

@@

Consistent with prior research on personality and political beliefs, participants in this study that were higher in economic conservatism produced significantly lower scores on openness to experience. This relationship has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience (Carney et al., 2008; Ekehammar et al., 2004).

However, inconsistent with prior research and our hypotheses, the negative relationship between social conservatism and openness to experience scores, along with the positive relationships between conscientiousness and both social and economic conservatism were not significant. With this subject so heavily studied, the lack of significant results indicates that a replication of the study that includes a power analysis and possibly, an increase in sample size may give us a clearer understanding of the strength and significance of these relationships.

Additional exploratory analysis revealed a significant positive relationship between emotional stability and social conservatism, as well as a positive relationship between agreeableness and social conservatism. Prior research indicates that emotional stability is not a significant predictor of conservatism, and agreeableness is usually negatively correlated with conservatism (Sibley, Osborne, \& Duckitt, 2012). The departure of these results from previous findings may indicate that there is an increase in positive personality traits associated with conservatism, but the controlling, firm, inhibited characteristics heavily associated with conservatism are not compatible with the change in direction between agreeableness and conservatism.

While the results of this study did not support all of our hypotheses on personality traits and conservatism, the limitations of the study surrounding the self-reporting methods along with the potential low power of the study may help explain the departure of our results from previous findings. Future research on this subject would be more informed through the use of experimental methods and observations of participants to determine behavior that reveals personality traits and level of social and economic conservatism. Increasing understanding of the relationship between personality traits and left-right differences could help implement actions that would help diffuse the increasing political polarization currently taking place in the United States.

@@

@@

\leavevmode\hypertarget{ref-barbaranelli2007voters}{}%
Barbaranelli, C., Caprara, G. V., Vecchione, M., \& Fraley, C. R. (2007). Voters' personality traits in presidential elections. \emph{Personality and Individual Differences}, \emph{42}(7), 1199--1208.

\leavevmode\hypertarget{ref-barlett2012direct}{}%
Barlett, C. P., \& Anderson, C. A. (2012). Direct and indirect relations between the big 5 personality traits and aggressive and violent behavior. \emph{Personality and Individual Differences}, \emph{52}(8), 870--875.

@@

\leavevmode\hypertarget{ref-carney2008secret}{}%
Carney, D. R., Jost, J. T., Gosling, S. D., \& Potter, J. (2008). The secret lives of liberals and conservatives: Personality profiles, interaction styles, and the things they leave behind. \emph{Political Psychology}, \emph{29}(6), 807--840.

@@

\leavevmode\hypertarget{ref-curtis2015relationship}{}%
Curtis, R. G., Windsor, T. D., \& Soubelet, A. (2015). The relationship between big-5 personality traits and cognitive ability in older adults--a review. \emph{Aging, Neuropsychology, and Cognition}, \emph{22}(1), 42--71.

\leavevmode\hypertarget{ref-ekehammar2004matters}{}%
Ekehammar, B., Akrami, N., Gylje, M., \& Zakrisson, I. (2004). What matters most to prejudice: Big five personality, social dominance orientation, or right-wing authoritarianism? \emph{European Journal of Personality}, \emph{18}(6), 463--482.

@@

\leavevmode\hypertarget{ref-goldberg1992development}{}%
Goldberg, L. R. (1992). The development of markers for the big-five factor structure. \emph{Psychological Assessment}, \emph{4}(1), 26.

@@

\leavevmode\hypertarget{ref-hayes2003big}{}%
Hayes, N., \& Joseph, S. (2003). Big 5 correlates of three measures of subjective well-being. \emph{Personality and Individual Differences}, \emph{34}(4), 723--727.

@@

\leavevmode\hypertarget{ref-hirsh2010compassionate}{}%
Hirsh, J. B., DeYoung, C. G., Xu, X., \& Peterson, J. B. (2010). Compassionate liberals and polite conservatives: Associations of agreeableness with political ideology and moral values. \emph{Personality and Social Psychology Bulletin}, \emph{36}(5), 655--664.

\leavevmode\hypertarget{ref-john1999big}{}%
John, O. P., \& Srivastava, S. (1999). The big five trait taxonomy: History, measurement, and theoretical perspectives. \emph{Handbook of Personality: Theory and Research}, \emph{2}(1999), 102--138.

\leavevmode\hypertarget{ref-jost2009personality}{}%
Jost, J. T., West, T. V., \& Gosling, S. D. (2009). Personality and ideology as determinants of candidate preferences and ``obama conversion'' in the 2008 us presidential election. \emph{Du Bois Review: Social Science Research on Race}, \emph{6}(1), 103--124.

\leavevmode\hypertarget{ref-mccrae1999age}{}%
McCrae, R. R., Costa, P. T., Lima, M. P. de, Simões, A., Ostendorf, F., Angleitner, A., \ldots{} others. (1999). Age differences in personality across the adult life span: Parallels in five cultures. \emph{Developmental Psychology}, \emph{35}(2), 466.

@@

\leavevmode\hypertarget{ref-R-GGally}{}%
Schloerke, B., Crowley, J., Cook, D., Briatte, F., Marbach, M., Thoen, E., \ldots{} Larmarange, J. (2018). \emph{GGally: Extension to 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=GGally}

\leavevmode\hypertarget{ref-sibley2012personality}{}%
Sibley, C. G., Osborne, D., \& Duckitt, J. (2012). Personality and political orientation: Meta-analysis and test of a threat-constraint model. \emph{Journal of Research in Personality}, \emph{46}(6), 664--677.

\leavevmode\hypertarget{ref-stenner2005rights}{}%
Stenner, P. (2005). Rights and emotions, or: The importance of having the right emotions. \emph{History \& Philosophy of Psychology}, \emph{7}(1), 1--11.
